A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
minor

\lstset{ 
	language=R,                     % the language of the code
	basicstyle=\ttfamily, % the size of the fonts that are used for the code
	numbers=left,                   % where to put the line-numbers
	numberstyle=\color{Blue},  % the style that is used for the line-numbers
	stepnumber=1,                   % the step between two line-numbers. If it is 1, each line
	% will be numbered
	numbersep=2pt,                  % how far the line-numbers are from the code
	backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
	showspaces=false,               % show spaces adding particular underscores
	showstringspaces=false,         % underline spaces within strings
	showtabs=false,                 % show tabs within strings adding particular underscores
	%frame=single,                   % adds a frame around the code
	rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
	tabsize=2,                      % sets default tabsize to 2 spaces
	captionpos=b,                   % sets the caption-position to bottom
	breaklines=true,                % sets automatic line breaking
	breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
	keywordstyle=\color{RoyalBlue},      % keyword style
	commentstyle=\color{YellowGreen},   % comment style
	stringstyle=\color{ForestGreen}      % string literal style
} 
\begin{document}

@@

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, some of them computer scientists, and
  did not find a single one aware of that fact. Library developers, on the
  other hand, tend to know about laziness and program defensively around
  it.}  Thus, our corpus distinguished between \emph{core packages} (there
are \miss{8} such packages that are loaded together with the R virtual
machine), \emph{CRAN packages} (we selected \miss{500} curated packages that
pass stringent community quality checks and are equipped with tests and
sample data), \emph{scripts} (we used \miss{400} end-user written programs
that performs a particular data analysis task).  There are reasons to
believe that \eval usage patterns may differ between these datasets. The
core R code is extremely stable, it has only been maintained for the last 20
years with very few far reaching changes. The libraries represent a more
lively ecosystem with new libraries added each day.  Finally, end user code
is often one-use scripts thrown together and sometimes never revisited.

>>>>

\lstset{ 
 language=R,              % the language of the code
 basicstyle=\small\ttfamily,    % the size of the fonts
% numbers=left,            % where to put the line-numbers
 numberstyle=\color{Blue},% the style that is used for the line-numbers
 stepnumber=1,            % the step between two line-numbers. If it is 1,
                          % each line will be numbered
 numbersep=2pt,           % how far the line-numbers are from the code
 backgroundcolor=\color{white},  % choose the background color.
 showspaces=false,        % show spaces adding particular underscores
 showstringspaces=false,  % underline spaces within strings
 showtabs=false,          % show tabs within strings adding particular 
%frame=single,            % adds a frame around the code
 rulecolor=\color{black}, % if not set, the frame-color may be changed on
                          % line-breaks within not-black text (e.g. commens
                          % (green here))
 tabsize=2,               % sets default tabsize to 2 spaces
 captionpos=b,            % sets the caption-position to bottom
 breaklines=true,         % sets automatic line breaking
 breakatwhitespace=false, % sets if automatic breaks should only happen at 
 keywordstyle=\color{Blue},    % keyword style
 commentstyle=\color{YellowGreen},  % comment style
 stringstyle=\color{ForestGreen}    % string literal style
} 
\begin{document}

@@

Our corpus has been constructed to reflect the different level of
sophistication in the R community. We distinguish between the core
implementers of the language, developers with both extensive programming
experience and keen understanding of the language semantics, library
implementers, developers with some programming experience and a working
knowledge of R, and end-users, who are typically not expert programmers and
often have only a cursory knowledge of the language.\footnote{To illustrate
  the above consider that R uses lazy evaluation like Haskell. The authors
  have informally surveyed end-users, including computer scientists, and did
  not find a single one aware of this fact. Library developers, on the other
  hand, know about laziness and program defensively around it.}  Thus, our
corpus distinguished between \emph{core packages} (there are \miss{8} such
packages that are loaded together with the R virtual machine), \emph{CRAN
  packages} (we selected \miss{500} curated packages that pass stringent
community quality checks and are equipped with tests and sample data),
\emph{scripts} (we used \miss{400} end-user written programs that performs a
particular data analysis task).  There are reasons to believe that \eval
usage patterns may differ between these datasets. The core R code is
extremely stable, it has only been maintained for the last 20 years with
very few far reaching changes. The libraries represent a more lively
ecosystem with new libraries added each day.  Finally, end user code is
often one-use scripts thrown together and sometimes never revisited.
